TBD

### 2021-02-20 outputs/paper/paper.Rmd
Add a bar chart for Q16

>>>>

```{r Q16, echo = FALSE, message = FALSE}
### Have you applied for and received any external funding or grants for your restaurant since (intervention start date)?
### Yes
### No

ggplot(data = all_simulated_dataset, mapping = aes(x = Q16, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Application status",
       y = "# of restaurants",
       title = str_wrap("Funding Applications between Oct 1 and Dec 31", 30),
       fill = "Condition") +
  theme_fivethirtyeight() +
  scale_fill_tableau(labels = c("Control", "Intervention"), guide = guide_legend(reverse = TRUE))
```
